% Paper template for TAR 2018
% (C) 2014 Jan Šnajder, Goran Glavaš, Domagoj Alagić, Mladen Karan
% TakeLab, FER

\documentclass[10pt, a4paper]{article}

\usepackage{tar2018}

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}

\title{Supercharged deep learning for a happier life}

\name{David Lozić, Luka Markušić} 

\address{
University of Zagreb, Faculty of Electrical Engineering and Computing\\
Unska 3, 10000 Zagreb, Croatia\\ 
\texttt{\{david.lozic,luka.markusic\}@fer.hr}\\
}
          
         
\abstract{ 
This document provides the instructions on formatting the TAR system description paper in \LaTeX{}. This is where you write the abstract (i.e., summary) of the work you carried out within the project. The abstract is a paragraph of text ranging between 70 and 150 words.
}

\begin{document}

\maketitleabstract

\section{Introduction}

Sentiment analysis (TODO: definiraj)

The very popular SemEval series hosts many sentiment analysis
competitions annually, with many different subtasks.
In recent years, the trend seems to follow deep learning models,
as they often occupy the top positions on the leaderboards.
At the very top of these competitions many elaborate models 
and complex ensambles can be found
which often provide a minor boost in performance.
Given that these models provide satisfactory performance,
we are interested in finding the minimal working model architecture
which still offers acceptable results.
The motivation behind this is to find the optimal industry oriented
model which would work well in a production environment.

This is made possible with the size of the dataset,
which provides us with the unique opportunity to do a detailed
architecture and hyperparameter analysis.
In essence, we perform an architecture and hyperparameter grid
search in pursuit of a lightweight model.



This section is the introduction to your paper. Introduction should not be too elaborate, as that is what other sections are for (the Introduction should definitely not spill over to the second page). 

This is the second paragraph of the introduction. In \LaTeX , paragraphs are separated by inserting an empty line in between them.  Avoid very large paragraphs (larger than half of the page height), but also avoid tiny paragraphs (e.g., one-sentence paragraphs).

\section{Related work}

Research in the area of sentiment analysis has usually focused on determining a given text's polarity, be it negative or positive, due to the lack of suitable annotated data. Even though the task of determining the emotion's intensity is challenging, it does not undermine the problematic task that is affect detection. A substantial number of approaches rely greatly on an underlying sentiment lexicon which, while being one of the most robust, is one of the most time-consuming methods. 

\section{Dataset/Resources}
The dataset for all of the tasks was provided by Mohammad \emph{et al} (2018), both in English, Spanish and Arabic. Out of total 173236 samples, X\% is English, Y\% Arabic, and the rest Spanish. Additional resources in form of word embeddigs and sentiment lexicons were provided by Stanford (GloVe) and National Research Council, Canada. 

\section*{Acknowledgements}

If suitable, you can include the \textit{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.

\bibliographystyle{tar2018}
\bibliography{tar2018} 

\end{document}

